\documentclass[11pt,a4paper,roman]{moderncv}      
\usepackage[english]{babel}
\moderncvstyle{classic}                            
\moderncvcolor{black}                            
\usepackage[utf8]{inputenc}                     
\usepackage[scale=0.80]{geometry}

\name{Shuolin (Leo) Yin}{}
\email{leo.yin@mail.utoronto.ca}
\phone[mobile]{+1 (647) 674-6127}               
\address{Toronto, ON, Canada}

\begin{document}

\recipient{To}{Hiring Manager \\
              Google STEP Internship Program}
\date{\today}
\opening{\textbf{Subject: Application for Google STEP Internship 2025}}
\closing{Best regards,}

\makelettertitle

Dear Hiring Manager,

I am a second-year Computer Engineering student at the University of Toronto, writing to express my strong interest in the Google STEP Internship for Summer 2025. With extensive experience in AI development and research, I am excited about the opportunity to contribute to Google's innovative technologies.

At CASIA, I am currently researching Multi-Modal Large Language Models, focusing on reducing hallucination problems and building automated data pipelines for model training. I've also led the development of an AI-powered travel planning platform at YiXing Software, where I implemented a Retrieval-Augmented Generation system using LangChain for personalized recommendations. These experiences have given me strong foundations in machine learning frameworks and practical AI application development.

Beyond AI, I've demonstrated my software development capabilities through VolunTrack, a full-stack platform I founded that serves 100+ non-profit organizations, and my role at IEEE UofT developing web applications and automation tools. These projects showcase my ability to build scalable solutions and work collaboratively in technical teams.

Thank you for considering my application.

\makeletterclosing

\end{document}