\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-5pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.05in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    \textbf{\Large \scshape Shuolin (Leo) Yin} \\ \vspace{5pt}
    \small +1 (647) 674-6127   $|$ 
    \href{mailto:shuolin.yin@gmail.com}{shuolin.yin@gmail.com} \\
    \href{https://github.com/leoyin1127}{https://github.com/leoyin1127} $|$
    \href{https://www.linkedin.com/in/shuolinyin/}{https://www.linkedin.com/in/shuolinyin/}
\end{center}

\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
  {University of Toronto}{Toronto, ON}
  {Computer Engineering, Faculty of Applied Science \& Engineering}{Sep 2023 -- Apr 2027}
  \resumeItemListStart
    \resumeItem{Faculty Of Applied Science And Engineering Admission Scholarship}
    \resumeItem{Edward S. Rogers Sr. Admission Scholarship}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheading
  {The Institute of Automation, Chinese Academy of Sciences (CASIA) }{Beijing, China}
  {Research Assistant}{May 2024 - Present}
  \resumeItemListStart
    \resumeItem{Co-authored research papers with the aiming of publishing in top conferences and journals in CVPR 2024 or Nature sub-journals.}
    \resumeItem{Investigated solutions to the hallucination problem in Multi-Modal large language models, including reviewing and synthesizing literature, proposing improvements, and attempting paper reproductions.}
    \resumeItem{Presented weekly progress reports to the research group, including proposed solutions and project updates.}
    \resumeItem{Completed advanced coursework, including Stanford's CS231n and Andrew Ng's Generative AI and LLM courses, to support project contributions.}
    \resumeItem{Contributed to building a benchmark for Multi-Modal Large Language Models (MLLM), including data collection and creating an automated pipeline for data segmentation and annotation.}
    % \resumeItem{Still Maintaining the confidentiality of the project's specific ideas and topics due to the planned publication of the research paper.}
  \resumeItemListEnd

\resumeSubheading
  {VolunTrack Org.}{Toronto, ON}
  {President/Founder}{Jun 2022 - Present}
  \resumeItemListStart
    \resumeItem{Founded the NGO with a four-tier management system, combined the organizational structure, formulated strategic guidelines and leading the rapid expansion with a leadership of 40+ people}
    \resumeItem{Secured a partnership with Google, have provided GCP credits and advanced technical training for 20+ members.}
    \resumeItem{Developed and iterated web/mobile applications using HTML, CSS, JavaScript, React Native, and React JS.}
    \resumeItem{Proficient in back-end database management, application version control, and front-end user interface design to enhance user experience}
    \resumeItem{Iterated to version 3.0.2 of the application through multiple CI/CD life cycles using Agile development methodology with continuous improvement and user feedback} 
    \resumeItem{Collaborated with over 100 non-profit organizations worldwide and serving as guest speaker at several seminars, offering students real-world project opportunities.}
  \resumeItemListEnd 
  
\resumeSubHeadingListEnd

\section{Project/School Experience}
\resumeSubHeadingListStart

\resumeSubheading
{IEEE UofT}{Toronto, ON}
{Web Team Associate}{Jun 2024 - Present}
\resumeItemListStart
  \resumeItem{Maintained and developed both backend and frontend for the IEEE UofT website and event-specific platforms.}
  \resumeItem{Developed and managed a hardware inventory and distribution platform, ensuring efficient tracking and management of resources.}
  \resumeItem{Implemented and maintained a Discord bot to automate and enhance member interactions and event coordination.}
  \resumeItem{Utilized technologies such as React JS for frontend development and Django for backend development.}
\resumeItemListEnd

  \resumeSubheading
  {YiXing Software Development}{Toronto, ON}
  {Project Leader / Co-Founder}{Jun 2023 - May 2024}
  \resumeItemListStart
    \resumeItem{Lead and create travel planning applications driven by fine-tuned LLM with a focus on personalized itineraries and sustainable tourism.}
    \resumeItem{Proficient in cross-platform mobile development using React Native and AI integration.}
    \resumeItem{Developed and fine-tuned a Retrieval-Augmented Generation (RAG) system, incorporating a vector database of previously generated plans for similarity matching, to enhance output efficiency and quality.}
    \resumeItem{Proficient in cloud computing and server management, using AWS and nodeJS for cloud and backend development}
  \resumeItemListEnd

\resumeSubHeadingListEnd

\section{Skills}
\resumeSubHeadingListStart
  \resumeSubItem{Programming Languages: JavaScript, C/C++, C\#, HTML, Python, Matlab, Swift.}
  \resumeSubItem{Tools/Frameworks: OpenCV, yolo, React Native, React JS, Node.js, jQuery, Xcode, Firebase, Google Cloud, AWS, Unity, LangChain, Git, VS Code, Fusion 360, Blender, AutoCAD, Xcode.}
\resumeSubHeadingListEnd

\end{document}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}
