\documentclass[11pt,a4paper,roman]{moderncv}      
\usepackage[english]{babel}
\moderncvstyle{classic}                            
\moderncvcolor{black}                            
\usepackage[utf8]{inputenc}                     
\usepackage[scale=0.80]{geometry}

\name{Shuolin (Leo) Yin}{}
\email{leo.yin@mail.utoronto.ca}
\phone[mobile]{+1 (647) 674-6127}               
\address{Toronto, ON, Canada}

\begin{document}

\recipient{To}{Taylor Walker \\
              Specialist, Internships \& Work Integrated Learning \\
              Vector Institute}
\date{\today}
\opening{\textbf{Subject: Application for Program Implementation Intern, AI Student Programs Position}}
\closing{Best regards,}

\makelettertitle

Dear Taylor Walker,

I am writing to express my strong interest in the Program Implementation Intern position for AI Student Programs at Vector Institute. As the founder of VolunTrack and an active participant in the AI ecosystem, I believe my experience in program coordination and event management aligns perfectly with this role.

At VolunTrack, I established a successful tech mentorship program that resulted in 30+ successful projects and 10+ conference speaking engagements. This experience has given me strong skills in program implementation, event coordination, and stakeholder management. I've created comprehensive documentation and training materials, tracked program metrics, and consistently delivered positive outcomes for participants – skills that directly align with the key responsibilities of this position.

My experience as a Research Assistant at CASIA has further enhanced my understanding of the AI ecosystem. I've led weekly technical discussions and authored comprehensive documentation to facilitate knowledge transfer across interdisciplinary teams. This experience has honed my ability to create detailed guides and toolkits, which would be valuable for equipping students with the knowledge and strategies needed for AI careers.

Additionally, my involvement in organizing hackathons, including leading the ReassurED project in Montreal, has given me practical experience in event planning and execution. I understand the importance of attention to detail, timeline management, and creating engaging experiences for participants.

I am particularly excited about the opportunity to contribute to the AI4Good 2025 program and AI Summit & Career Fair. My technical background in AI, combined with my program coordination experience, positions me well to help deliver impactful outcomes for these initiatives.

Thank you for considering my application. I look forward to discussing how I can contribute to Vector Institute's mission of building a strong and diverse AI ecosystem in Canada.

\makeletterclosing

\end{document}