\documentclass[11pt,a4paper,roman]{moderncv}      
\usepackage[english]{babel}
\moderncvstyle{classic}                            
\moderncvcolor{black}                            
\usepackage[utf8]{inputenc}                     
\usepackage[scale=0.80]{geometry}

\name{Shuolin (Leo) Yin}{}
\email{leo.yin@mail.utoronto.ca}
\phone[mobile]{+1 (647) 674-6127}               
\address{Toronto, ON, Canada}

\begin{document}

\recipient{To}{Taylor Walker \\
              Specialist, Internships \& Work Integrated Learning \\
              Vector Institute}
\date{\today}
\opening{\textbf{Subject: Application for Applied AI Program Design \& Delivery Intern Position}}
\closing{Best regards,}

\makelettertitle

Dear Taylor Walker,

I am writing to express my strong interest in the Applied AI Program Design \& Delivery Intern position at Vector Institute. With my experience in AI education, technical communication, and program management, I am excited about the opportunity to contribute to Vector's industry innovation initiatives.

At CASIA, I spearhead weekly technical discussions between medical experts and ML researchers, effectively translating complex AI concepts for diverse audiences. I've developed comprehensive research documentation and training materials that bridge the gap between technical and non-technical stakeholders. This experience has honed my ability to communicate AI concepts clearly and design engaging educational content.

As the founder of VolunTrack, I established a successful tech mentorship program that has resulted in 30+ successful projects and 10+ conference speaking engagements. This experience involved designing curriculum, coordinating workshops, and managing program logistics – skills that directly align with the key responsibilities of this position. I've also tracked program metrics and created comprehensive reports to demonstrate impact and inform future improvements.

My current research work on Medical multimodal large language models (MLLMs) keeps me at the forefront of AI developments, enabling me to identify relevant use cases and content for industry programs. Through projects like ReassurED and YiXing, I've gained practical experience applying ML techniques to real-world problems, which would be valuable in designing industry-focused AI education programs.

I am particularly excited about the opportunity to contribute to Vector's mission of facilitating industry adoption of AI. My combination of technical expertise and program management experience positions me well to support the design and delivery of impactful AI upskilling initiatives.

Thank you for considering my application. I look forward to discussing how I can contribute to Vector Institute's industry innovation programs.

\makeletterclosing

\end{document}