\documentclass[11pt,a4paper,roman]{moderncv}      
\usepackage[english]{babel}
\moderncvstyle{classic}                            
\moderncvcolor{black}                            
\usepackage[utf8]{inputenc}                     
\usepackage[scale=0.80]{geometry}

\name{Shuolin (Leo) Yin}{}
\email{leo.yin@mail.utoronto.ca}
\phone[mobile]{+1 (647) 674-6127}               
\address{Toronto, ON, Canada}

\begin{document}

\recipient{To}{Dr. Enid Montague \\
              Department of Mechanical \& Industrial Engineering \\
              University of Toronto}
\date{\today}
\opening{\textbf{Subject: Application for Healthcare Engineering Research Position}}
\closing{Best regards,}

\makelettertitle

Dear Dr. Montague,

I am writing to express my strong interest in the Healthcare Engineering Research position in the Department of Mechanical \& Industrial Engineering at the University of Toronto. As a current Computer Engineering student at UofT with extensive experience in healthcare AI research and automation, I am excited about the opportunity to contribute to research exploring automation in caregiving and cardiac care.

My previous role as a Research Assistant at the Institute of Automation, Chinese Academy of Sciences has provided me with valuable experience in healthcare technology research. I have developed end-to-end data pipelines for medical imaging benchmarks and implemented multimodal evaluation frameworks for clinical medicine applications. This experience has given me a strong foundation in both the technical and human-centered aspects of healthcare automation research.

I am particularly drawn to the position's focus on human subjects studies and evaluation research. Through my work on ReassurED, an AI-powered emergency care navigator, I gained practical experience in designing and implementing healthcare systems that consider both technical efficiency and user experience. The project involved extensive interaction with medical professionals and patients, giving me insight into the importance of human factors in healthcare automation.

As a UofT Engineering student, I am familiar with the university's research environment and am eager to contribute to the department's innovative work. I am particularly interested in the opportunity to participate in design and observational research, areas where I can apply both my technical skills and understanding of human-centered design principles.

I appreciate your consideration of my application and look forward to discussing how I can contribute to your research in healthcare automation and caregiving.

\makeletterclosing

\end{document}