\documentclass[11pt,a4paper,roman]{moderncv}      
\usepackage[english]{babel}
\moderncvstyle{classic}                            
\moderncvcolor{black}                            
\usepackage[utf8]{inputenc}                     
\usepackage[scale=0.80]{geometry}

\name{Shuolin (Leo) Yin}{}
\email{shuolin.yin@gmail.com}
\phone[mobile]{+1 (647) 674-6127}               
\address{Toronto, ON, Canada}

\begin{document}

\recipient{To}{Hiring Manager \\
               Clean Energy Innovation Research Centre \\
               National Research Council Canada \\
               Mississauga, ON}
\date{\today}
\opening{\textbf{Subject: Application for Research Assistant, AI/ML Software Development and Integration Position (Job ID: 33631)}}
\closing{Sincerely,}

\makelettertitle

Dear Hiring Manager,

I am writing to express my strong interest in the Research Assistant position at the National Research Council Canada's Clean Energy Innovation Research Centre. As a Computer Engineering student at the University of Toronto with substantial experience in AI/ML research and software development, I am excited about the opportunity to contribute to NRC's mission of developing green and sustainable technologies.

My current role as a Research Assistant at the Chinese Academy of Sciences has provided me with directly relevant experience in AI/ML development. I have been actively involved in developing and implementing machine learning models, particularly focusing on Multi-Modal Large Language Models. This experience has helped me develop strong skills in Python programming, experimental design, and working with modern ML frameworks like PyTorch.

The position's requirements align well with my technical expertise and experiences:

\begin{itemize}
\item As the founder of VolunTrack, I've led the development of modular software systems and implemented automated pipelines for data processing, demonstrating my proficiency in object-oriented programming and software design patterns.
\item Through my work at IEEE UofT, I've gained hands-on experience with collaborative software development using Git and contributing to large-scale projects.
\item My experience with YiXing Software Development involved implementing AI systems and conducting literature reviews to identify and integrate new capabilities, skills directly relevant to the research aspects of this position.
\end{itemize}

I am particularly excited about the opportunity to contribute to NRC's green technology initiatives. The chance to apply my AI/ML expertise to accelerate materials research and contribute to Canada's clean economy aligns perfectly with my career goals and interests in sustainable technology.

As a Computer Engineering student enrolled in a co-op program at the University of Toronto, I meet all the eligibility requirements for this position. I maintain above a B average and am authorized to work in Canada.

I would welcome the opportunity to discuss how my skills and experiences align with NRC's needs in more detail. Thank you for considering my application.

\makeletterclosing

\end{document}