\documentclass[11pt,a4paper,roman]{moderncv}      
\usepackage[english]{babel}
\moderncvstyle{classic}                            
\moderncvcolor{black}                            
\usepackage[utf8]{inputenc}                     
\usepackage[scale=0.80]{geometry}

\name{Shuolin (Leo) Yin}{}
\email{leo.yin@mail.utoronto.ca}
\phone[mobile]{+1 (647) 674-6127}               
\address{Toronto, ON, Canada}

\begin{document}

\recipient{To}{Hiring Manager \\
              Google Student Researcher Program}
\date{\today}
\opening{\textbf{Subject: Application for Google Student Researcher Program}}
\closing{Best regards,}

\makelettertitle

Dear Hiring Manager,

I am a second-year Computer Engineering student at the University of Toronto, writing to express my interest in the Google Student Researcher Program. With hands-on research experience in Multi-Modal Large Language Models and a strong foundation in machine learning, I am excited about the opportunity to contribute to Google's research initiatives.

At the Institute of Automation, Chinese Academy of Sciences (CASIA), I am actively researching solutions to reduce hallucination in Multi-Modal Large Language Models, with work planned for publication at ECCV 2025. My responsibilities include developing automated data pipelines, conducting model experiments, and contributing to benchmark creation for MLLMs. This experience has given me strong foundations in Python, PyTorch, and machine learning methodologies.

I have also demonstrated practical applications of AI research through my work at YiXing Software, where I implemented a Retrieval-Augmented Generation system for personalized travel planning. This project involved applying research concepts to solve real-world problems, aligning with Google's mission of developing solutions for large-scale challenges.

I am particularly interested in the opportunity to collaborate on research projects at Google, especially in the areas of natural language understanding and machine learning. As a student planning to continue my academic program after the internship, I am eager to contribute to Google's research community while gaining valuable industry research experience.

Thank you for considering my application.

\makeletterclosing

\end{document}