\documentclass[11pt,a4paper,roman]{moderncv}      
\usepackage[english]{babel}
\moderncvstyle{classic}                            
\moderncvcolor{black}                            
\usepackage[utf8]{inputenc}                     
\usepackage[scale=0.80]{geometry}

\name{Shuolin (Leo) Yin}{}
\email{leo.yin@mail.utoronto.ca}
\phone[mobile]{+1 (647) 674-6127}               
\address{Toronto, ON, Canada}

\begin{document}

\recipient{To}{Taylor Walker \\
              Specialist, Internships \& Work Integrated Learning \\
              Vector Institute}
\date{\today}
\opening{\textbf{Subject: Application for Health AI Intern Position}}
\closing{Best regards,}

\makelettertitle

Dear Taylor Walker,

I am writing to express my keen interest in the Health AI Intern position at Vector Institute. As a Computer Engineering student at the University of Toronto with substantial experience in healthcare AI research and project management, I am excited about the opportunity to contribute to Vector's mission of advancing AI applications in healthcare.

My current role as a Research Assistant at CASIA has given me direct experience in healthcare AI applications, where I'm working on Medical multimodal large language models (MLLMs) for enhanced diagnosis reliability. I've developed end-to-end data pipelines for medical imaging benchmarks, resulting in a 75\% reduction in processing time and 40\% improvement in annotation accuracy. This experience aligns perfectly with Vector's focus on applying AI to real-world health problems.

As the founder of VolunTrack, I've demonstrated strong project management capabilities by leading a team of 50+ members and establishing partnerships with over 100 organizations. I've created project plans, implemented monitoring systems, and coordinated cross-functional teams – skills that directly match the key responsibilities outlined for this position. Additionally, my experience developing ReassurED, an AI-powered emergency care guidance system, has given me valuable insights into healthcare data management and privacy considerations.

I am particularly drawn to Vector's commitment to building a strong and diverse AI ecosystem in Canada. I am excited about the opportunity to contribute to Vector's health projects while learning from and collaborating with experts in the field.

Thank you for considering my application. I look forward to discussing how I can contribute to Vector Institute's important work in advancing health AI applications.

\makeletterclosing

\end{document}