\documentclass[11pt,a4paper,roman]{moderncv}      
\usepackage[english]{babel}
\moderncvstyle{classic}                            
\moderncvcolor{black}                            
\usepackage[utf8]{inputenc}                     
\usepackage[scale=0.80]{geometry}
\name{Shuolin (Leo) Yin}{}
\email{leo.yin@mail.utoronto.ca}
\phone[mobile]{+1 (647) 674-6127}               
\address{Toronto, ON, Canada}
\begin{document}
\recipient{To}{Hiring Manager \\
              CIBC Technology}
\date{\today}
\opening{\textbf{Software/Application Developer Co-op}}
\closing{Best regards,}
\makelettertitle
Dear Hiring Manager,

I am a third-year Computer Engineering student at the University of Toronto, excited to apply for the Software/Application Developer Co-op position. With hands-on experience in Python, Java, and Linux environments building cross-functional, multi-platform systems, I am eager to contribute to CIBC's digital transformation.

At Medical3.ai, I architected systems coordinating across multiple workflows, collaborating with stakeholders to translate business requirements into technical specifications, reducing research time by 70\%. At Lumi AI, I shipped a full-stack platform with Node.js and PostgreSQL, implementing authentication and audit logging for sensitive data. These experiences have prepared me to develop, test, and debug reliable applications at scale.

I thrive taking ownership in collaborative environments. Whether coordinating with clinicians at Vector Institute or leading a team to 2nd place globally at BCG Hack the Globe, I bring both technical depth and the communication skills to work effectively across teams. I am drawn to CIBC's values of trust, teamwork, and accountability, and would welcome the opportunity to discuss how I can contribute to your technology initiatives.

Thank you for considering my application.

\makeletterclosing
\end{document}