\documentclass[11pt,a4paper,roman]{moderncv}      
\usepackage[english]{babel}
\moderncvstyle{classic}                            
\moderncvcolor{black}                            
\usepackage[utf8]{inputenc}                     
\usepackage[scale=0.80]{geometry}

\name{Shuolin (Leo) Yin}{}
\email{leo.yin@mail.utoronto.ca}
\phone[mobile]{+1 (647) 674-6127}               
\address{Toronto, ON, Canada}

\begin{document}

\recipient{To}{Taylor Walker \\
              Specialist, Internships \& Work Integrated Learning \\
              Vector Institute}
\date{\today}
\opening{\textbf{Subject: Application for Applied Machine Learning Intern Position}}
\closing{Best regards,}

\makelettertitle

Dear Taylor Walker,

I am writing to express my strong interest in the Applied Machine Learning Intern position at Vector Institute. As a Computer Engineering student at the University of Toronto with extensive experience in AI development and research, I am excited about the opportunity to contribute to Vector's mission of applying AI research to real-world problems.

At CASIA, I'm currently working on Medical multimodal large language models (MLLMs), where I've implemented and evaluated SOTA architectures using PyTorch, focusing on cross-modal attention mechanisms and medical knowledge integration. I've also engineered an end-to-end data pipeline for medical imaging benchmarks, resulting in a 75\% reduction in processing time and 40\% improvement in annotation accuracy. This experience has given me practical skills in handling real-world data and developing production-ready AI solutions.

My project portfolio demonstrates my ability to apply AI research to practical applications. At ReassurED, I implemented a dynamic triage system using Few-shot Learning with Deepseek-v3, while at YiXing, I designed and implemented a Retrieval-Augmented Generation (RAG) system using LangChain and vector databases. Both projects required working with messy real-world data and developing scalable solutions using modern AI frameworks.

I have extensive experience with Python, PyTorch, and TensorFlow, and I'm well-versed in agile development methodologies through my work at VolunTrack, where I led the development of a full-stack platform serving 100+ organizations. I'm particularly interested in large language models and deep generative models, as demonstrated by my current research work.

I am excited about the opportunity to work alongside Vector's AI developers and researchers, contributing to open-source software development and helping to solve industry challenges. My combination of technical skills, research experience, and practical application development makes me well-suited for this role.

Thank you for considering my application. I look forward to discussing how I can contribute to Vector Institute's innovative AI projects.

\makeletterclosing

\end{document}